---
title: "Parkrun"
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  echo=FALSE,warning = FALSE, message = FALSE,
  comment = "#>"
)

librarian::shelf(
  dplyr,data.table,
  lubridate, stringr, 
  sf, 
  mapgl, ggplot2,plotly,flextable,htmltools,viridis
  )

source("scriptsR/parkrun/dataproc_map_tabs.R")

```

[Home](index.qmd) 

[On the parkrun website](https://www.parkrun.org.uk/parkrunner/4452710/all/)

:::

Parkrun is a free and open community event, a 5k race taking place on Saturdays at 9am across many parks in the world. I have been parkrunning since 2017 or so. I plot some of my history below.

I am undertaking a challenge to run one parkrun in each of the 32 boroughs of Greater London, progress shown in the map.

:::

::: {.panel-tabset .nav-pills}

## Timeline

```{r}
timeline_evently
```

## Borough Challenge

<p>Show events ran and nearby, click on the circle for location results</p>
```{r}
map
```

## All results

```{r}
htmltools_value(ft)
```

## Overview

```{r}

htmltools::HTML(
  paste0(
    "<p>Participated in ", total_summary$Events, " events running ",
    total_summary$Kilometers, " kilometers in ", total_summary$TotalTime,
    " with a median runtime of ", total_summary$MedianTime, ".</p>"
  )
)

# Display summaries side by side
htmltools::div(
  style = "display: flex; gap: 20px; justify-content: space-evenly;",
  htmltools_value(tbe),
  htmltools_value(tby)
)

```

:::
